Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-12-04 tex/MISDP-Presolving/MISDPpresolving.tex
minor extension of argument

% -------------------------------------------------------------------------
\subsection{Implied Linear Inequalities}

@@

\begin{lemma}
  For any solution $y \in \R^m$ of~\eqref{MISDP}, we have
  \[
    -\sqrt{\tilde{U}_{ii}\,\tilde{U}_{jj}} \leq A(y)_{ij} \leq \sqrt{\tilde{U}_{ii}\,\tilde{U}_{jj}}
  \]
  for all $i$, $j \in [n]$.
\end{lemma}

@@

@@

\begin{lemma}
  $f(\mu)$ is concave.
\end{lemma}

\begin{proof}
  We have for $\alpha \in [0,1]$ and $\mu_1$, $\mu_2 \geq 0$:
  \begin{align*}
    f\big(\alpha \mu_1 + (1 - \alpha) \mu_2\big)
    & = \lambda_{\min}\big((\alpha \mu_1 + (1 - \alpha) \mu_2) A^k - A^0\big)\\
    & = \lambda_{\min}\big(\alpha (\mu_1\, A^k - A^0) + (1 - \alpha) (\mu_2\, A^k - A^0)\big)\\
    & \geq \lambda_{\min}\big(\alpha (\mu_1\, A^k - A^0)\big) + \lambda_{\min}\big((1 - \alpha) (\mu_2\, A^k - A^0)\big)\\
    & = \alpha\, \lambda_{\min}\big(\mu_1\, A^k - A^0\big) + (1 - \alpha)\, \lambda_{\min}\big(\mu_2\, A^k - A^0\big)\\
    & = \alpha\, f(\mu_1) + (1 - \alpha)\, f(\mu_2),
  \end{align*}
  which shows the claim.
\end{proof}

>>>>

% -------------------------------------------------------------------------
\subsection{Implied Linear Inequalities}\label{sec:ImpliedLinEqs}

@@

\begin{lemma}\label{lem:Propagation}
  For any solution $y \in \R^m$ of~\eqref{MISDP}, we have
  \[
    -\sqrt{\tilde{U}_{ii}\,\tilde{U}_{jj}} \leq A(y)_{ij} \leq \sqrt{\tilde{U}_{ii}\,\tilde{U}_{jj}}
  \]
  for all $i$, $j \in [n]$.
\end{lemma}

@@

\begin{remark}
  Note that in the pure form, the propagated inequalities from
  Lemma~\ref{lem:Propagation} dominate the inequalities given in
  Section~\ref{sec:ImpliedLinEqs}:
  \begin{align*}
    X_{st} \leq \sqrt{U_{ss} \cdot U_{tt}} \leq \frac{1}{2}\big( U_{ss} + U_{tt}\big),
  \end{align*}
  because of the inequality between the arithmetic and geometric mean. Does
  this also hold in the general case of a (dual) LMI?
\end{remark}

@@

\begin{lemma}
  For any two symmetric matrices $A^k$, $A^0 \in \R^{n \times n}$, the function
  $f(\mu) = \lambda_{\min}(\mu\, A^k - A^0)$ is concave.
\end{lemma}

\begin{proof}
  We have for $\alpha \in [0,1]$ and $\mu_1$, $\mu_2 \geq 0$:
  \begin{align*}
    f\big(\alpha \mu_1 + (1 - \alpha) \mu_2\big)
    & = \lambda_{\min}\big((\alpha \mu_1 + (1 - \alpha) \mu_2) A^k - A^0\big)\\
    & = \lambda_{\min}\big(\alpha (\mu_1\, A^k - A^0) + (1 - \alpha) (\mu_2\, A^k - A^0)\big)\\
    & \geq \lambda_{\min}\big(\alpha (\mu_1\, A^k - A^0)\big) + \lambda_{\min}\big((1 - \alpha) (\mu_2\, A^k - A^0)\big)\\
    & = \alpha\, \lambda_{\min}\big(\mu_1\, A^k - A^0\big) + (1 - \alpha)\, \lambda_{\min}\big(\mu_2\, A^k - A^0\big)\\
    & = \alpha\, f(\mu_1) + (1 - \alpha)\, f(\mu_2).
  \end{align*}
  The inequality follows because for a symmetric matrix~$C \in \R^{n \times n}$:
  \[
    \lambda_{\min}(C) = \min_{\norm{x} = 1} x\T C x.
  \]
  Thus, for a symmetric matrix $D \in \R^{n \times n}$
  \begin{align*}
    \lambda_{\min}(C + D) & = \min_{\norm{x} = 1} x\T (C + D) x\\
    & \geq \min_{\norm{x} = 1} x\T C  x + \min_{\norm{x} = 1} x\T D x =
    \lambda_{\min}(C) + \lambda_{\min}(D),
  \end{align*}
  which shows the inequality.
\end{proof}
